\textbf{Response Letter}

### 2018-12-24 doc/aij18/major-revision/background.tex

\textcolor[rgb]{1.00,0.00,0.00}{In \FAMA, we need to implicitly represent the unobserved literals of states. In order to do so, we will adopt the \emph{open world assumption}; i.e., what is not known to be true in a state is unknown. Consequently, states will explicitly include positive literals ($f$) and negative literals ($\neg f$) such that literals that are not in a state are unknown or unobserved.} Hence, a {\em state} $s$ is a full assignment of values to fluents; i.e. $|s|=|F|$, so the size of the state space is $2^{|F|}$. Like in PDDL~\cite{fox2003pddl2}, we assume that fluents $F$ are instantiated from a set of {\em predicates} $\Psi$. Each predicate $p\in\Psi$ has an argument list of arity $ar(p)$. Given a set of {\em objects} $\Omega$, the set of fluents $F$ is induced by assigning objects in $\Omega$ to the arguments of predicates in $\Psi$; i.e.~$F=\{p(\omega):p\in\Psi,\omega\in\Omega^{ar(p)}\}$ such that $\Omega^k$ is the $k$-th Cartesian power of $\Omega$.

@@

================

A plan trace $\tau = \langle s_0, a_1, s_1, a_2, s_2, \ldots, a_n, s_n \rangle$ for a planning frame $\Phi=\tup{F,A}$ holds that $a_i\in A$ for every action in $\tau$ and that $s_i \in \mathcal{L}(F)$ for each {\small $1\leq i\le n$}.

NO TENGO CLARO LO QUE QUEREMOS DECIR CON ESTA FRASE (??). ADEMAS, NO ES CORRECTA PORQUE LOS ESTADOS DE UNA TRAZA PUEDEN SER FULL-OBSERVABLE Y $\mathcal{L}(F)$ SON PARTIAL ASSIGNMENTS OF VALUES TO FLUENTS.

=================

Plan traces can be classified accordingly to the type of observed state trajectory (\FO, \POstar, \PO or \NO) and action sequence (\FO, \PO or \NO). \textcolor[rgb]{1.00,0.00,0.00}{In section \ref{overview}, we expose the impact of all combinations of observed state trajectories and observed action sequences in the complexity of the learning task.}

@@

Most approaches assume that a set of predicates and a set of action headers are provided alongside the input traces. Others do not explicitly say so but the fact is that predicates and actions headers are easily extractable from the state sequence and action sequence of the input plan traces, respectively. A requirement, however, is that the input plan traces comprise at least a grounded sample of every predicate and operator schema in the domain model.

@@

In the following, we present a comprehensive insight of the particularities of the seven systems presented in Table \ref{table:models_comparison1} and Table \ref{table:models_comparison2}. This exposition will help us to highlight in section \ref{sec:motivation} the value of our contribution \FAMA.

@@

\textcolor[rgb]{1.00,0.00,0.00}{The distinctive feature of \LOCMtwo lies in the need to learn the state variables (fluents) because predicates are not either provided as input nor they are deducible from the plan trace as no state observability is allowed. In contrast, \FAMA and the rest of approaches either assume the set of predicates are provided alongside the input traces or assume they are extractable from the observed states of the plan trace, in which case the plan trace must comprise at least a grounded sample of every predicate. Similarly, the syntax of an action header (the action name and its parameters) is either extractable from the action sequence of the plan trace or it must be explicitly provided.}

>>>>

\textcolor[rgb]{1.00,0.00,0.00}{We will adopt the \emph{open world assumption}, that is, what is not known to be true in a state is unknown, to implicitly represent the unobserved literals of states. Consequently, states will explicitly include positive literals ($f$) and negative literals ($\neg f$) such that literals that are not in a state are unknown or unobserved.} Hence, a {\em state} $s$ is a full assignment of values to fluents; i.e. $|s|=|F|$, so the size of the state space is $2^{|F|}$. Like in PDDL~\cite{fox2003pddl2}, we assume that fluents $F$ are instantiated from a set of {\em predicates} $\Psi$. Each predicate $p\in\Psi$ has an argument list of arity $ar(p)$. Given a set of {\em objects} $\Omega$, the set of fluents $F$ is induced by assigning objects in $\Omega$ to the arguments of predicates in $\Psi$; i.e.~$F=\{p(\omega):p\in\Psi,\omega\in\Omega^{ar(p)}\}$ such that $\Omega^k$ is the $k$-th Cartesian power of $\Omega$.

@@

Plan traces can be classified accordingly to the type of observed state trajectory (\FO, \POstar, \PO or \NO) and action sequence (\FO, \PO or \NO). \textcolor[rgb]{1.00,0.00,0.00}{In section \ref{task_definition}, we expose the impact of the combinations of observed state trajectories and observed action sequences when solving a learning task.}

@@

%Most approaches assume that a set of predicates and a set of action headers are provided alongside the input traces. Others do not explicitly say so but the fact is that predicates and actions headers are easily extractable from the state sequence and action sequence of the input plan traces, respectively. A requirement, however, is that the input plan traces comprise at least a grounded sample of every predicate and operator schema in the domain model.

@@

In the following, we present a comprehensive insight of the particularities of the seven systems presented in Table \ref{table:models_comparison1} and Table \ref{table:models_comparison2}. This exposition will also help us to highlight in section \label{task_definition} the value of our contribution \FAMA.

@@

\textcolor[rgb]{1.00,0.00,0.00}{The distinctive feature of the \LOCM family lies in the need to learn the state variables (fluents) because predicates are neither provided as input nor they are deducible from the plan trace as no state observability is allowed. In contrast, \FAMA and the rest of approaches either assume the set of predicates are provided alongside the input traces or assume they are extractable from the observed states of the plan trace, in which case the plan trace must comprise at least a grounded sample of every predicate. Similarly, the syntax of an action header (the action name and its parameters) is either extractable from the action sequence of the plan trace or it must be explicitly provided.}
